Reanalysis Step 7: Missingness Pattern Analysis

### 2025-09-01 reanalysis-7-missingness_patterns.qmd
better diagnostics for missingness

# Load imputed datasets to get the included sample
imputed_datasets <- list()
for (i in 1:20) {
  imputed_datasets[[i]] <- readRDS(file.path(reanalysis_data_dir, paste0("imputed_dataset_", i, ".rds")))
}

>>>>

# Load imputed datasets (this is a list of 20 imputed dataframes)
imputed_datasets <- readRDS(file.path(reanalysis_data_dir, "imputed_datasets.rds"))
